\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
%\usepackage[swedish]{babel}
\usepackage{lmodern}
\usepackage[parfill]{parskip}
\usepackage[pdftex,
            pdfauthor={Oscar Bohlin},
            pdftitle={Defining The Decade}]{hyperref}


\hypersetup{pdfborder = {0 0 0}}
\title{Defining The Decade}
\date{10/03/2019}
\author{Oscar Bohlin}

\begin{document}

\pagenumbering{gobble}
\maketitle
\newpage
\pagenumbering{arabic}
\tableofcontents
\newpage


\section{Introduction}

    This decade began on the ninht of september, 2001, when Usama ibn Ladin ordered the attack of the Twin Tower. The decade began with destruction and wars against terrorism. WHat started with American dominance is now comming to and end with a new economical superpower, China. 


\section{Summary}

    Ever since 11/9/2001, the USA has been all over the world proving their dominance. Intrusions in Afghanistan and Iraq to stop terrorism was a big part of USA's agenda until a new enemy emerged from the shadows, China. The USA has since a long time been the worlds most powerful nation, from the military and economic standpoint, and when the USA cannot reuse the same method on terrorism on China, they must change strategy, but to which? The country is still recovering from the devestating consequences from Iraq and Afghanistan with the high mortality rate of the soldiers and civilians. The USA struggles to find it's place in an area they're not so familiar with, diplomacy.  



\section{My thoughts}

    At 41 minutes and 54 seconds. This podcast really challenged my focus. I think this podcast way more longer than what it needed to be, I felt think it included too many parts what were too specific and that didn't have their place in the podcast. An example of this is the speculation that terrorist (I do not remember which organisation) were in control of weapons of mass destructions. Which indeed is a scary thought but I found it unnecessary to the plot. 

    It included too many details causing me too lose focus of what the actual story was, and i think they should've focus more on the conflict between China and the USA instead. However, overall it was a okay podcast, nothing too particular, it had an intresting topic with poor execution.  

\end{document}