\documentclass[a4paper,12pt]{article}
%\usepackage[swedish]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{chemformula}
\usepackage{amsmath}
\usepackage[parfill]{parskip}
%\usepackage[pdftex,
 %           pdfauthor={Oscar Bohlin},
  %          pdftitle={The Heart Has Its Reason}]{hyperref}
%\usepackage{apacite}
%\usepackage[style=apa,backend=biber]{biblate}
%\bibliography{källor}
%\addbibresource{biblatex-examples.bib}
%\bibliography{biblatex-examples}
%\hypersetup{pdfborder = {0 0 0}}

\title{The Heart Has It's Reason}
\author{Oscar Bohlin}
\date{07-03-2019}

\begin{document}
\pagenumbering{gobble}
\maketitle
\newpage
\pagenumbering{arabic}
\tableofcontents
\newpage
%   Poetry, language, think with heart, not brain. Spirituell level 
%   Pumping blood, biological purpose
%The hert contains nervcells, same type as the brain, could in theory store memory. Some "heart memory storage"  can be transfered when a heart transsplant recives a new heart. 
%
%   This could be explained by the human overthinking or placebo effects.                   

\section{Introduction}

    The heart, one of the bodies most crucial organs, with the taks of keeping us alive by rythmic contractions through our whole life, is often in the centre in poetry and other spirituous activities. What is the true function the brain? This question is investigated by the $BBC^1$ and features many different perspetives on the hearts function. 

\section{Summary}

    Throughout the podcast, we are introduced to different perspectives and functionalites of the heart. In the beginning, we are introduced to the lifesubstaining functionality, without the heart we cannot survive. However, the heart contains nervcells that are identical to the ones in the brain, meaing in theory we could store memories in the heart. While this remains to be a controvecial topic one cannot ignore the fact we can trasfer memories with heart transplants. The heart is often in centrum in spiritual thought, that the heart store ones soul and has more meaning than just keeping us alive. 

\section{My thoughts}

I did not find this podcast particular intresting. I find it unintresting because it was mainly speculation, no proof of anything was portrayed, only speculation of reasons behind an incident. For an example the patient who became obsessed with a particular date, only to find out it was the birthday of the donor. When you take it out of context it seems like the heart transplant was the cause, but in realiyt it can be whatever. The podcast didn't have any foundation to lay their "grouds", only stated their explanation. It did however include doctors not trusting this phenomenon. But in short, it was only speculations.


\end{document}